A thesis draft

### 2018-10-10 draft.tex
Minor fix about SFC packet transmission

As today, when a packets gets send from a seder $S$, to a receiver $R$, the 
packet gets travelling to te backbone receive appropriate in-hardware packet 
processing before being received by $R$. During this elaboration, it is 
important to maintain the transparency of the connection, so that the network 
users are not aware of the packets elaboration at all. To perform that, many 
solutions are available: TUN/TAP packet incapsulation, IP over IP or TCP 
session recreation (know also as TCP split).

TUN/TAP and IP over IP maintain the connection transparency incapsulating the
packet in another one.
\begin{figure}[t]
  \centering
  \includegraphics[scale=0.5]{IPoverIP}
  \caption[IP over IP schema]{An example of IP over IP. Is noticeable how the
    original packet becomes the payload of a new one, thus being encapsulated.
    All the informations regarding the original packet remains untouched: when
    this kind of packet gets send from a machine to another, the OS will remove
    the new packet header and will present to the user-space program receiving
    the data its payload: a IP packet. Packets encapsulation can be applied with
    higher layers too, thus allowing for TCP and UDP packet incapsulation.}
  \label{chap:prjan:img:ip_over_ip}
\end{figure}

In this way, the original packet remains preserved and it becomes the new packet
payload\todo{Make an image showing a packet inside another packet, to make easy
  to understand what we're meaning here}, that can be elaborated and modified
accordingly, until it gets decapsulated and sent to $R$ eventually. When $R$
receives the packet, it is not be aware of the packet elaboration, since all the
original headers were preserved (or slightly modified). TCP session recreation,
instead, ``split'' the TCP session in two endpoints: an Ingress, that manage the
connection with the client and an Egress, that communicate with the packet
receiver creating a multi-overlay-hop path where for each hop there is an
possible indipendent TCP connection. In order to achieve that, a session table
needs to be established and continuously updated, while TCP headers need to be
accordingly modified to allow data transmission through the Ingress and Egress
points. Nonetheless, care should be given to packets path: in order to avoid
ill-calculated congestion windows, the incoming packets need to follow the same
(or an equivalent one) path for the same instatiated connection. This phenomenom
is based on the intermediate proxies that create the route: it is the case, for
example, when an intermediate node sends back a spoofed ACK before the original
packet is delivered to the real consegnee. In this senario, the sender, unaware
of the proxy, will miscalculate the sending window based on the too low RTT.
Other problems of TCP splitting are reliability and security, especially because
the end to end TCP logic is no longer maintained: a server failure may cause to
an unaware client to believe that all the packets have reached the destination.
TCP session recreation seems burdersome and it doesn't seem to add any
significant benefit at the first sight, but it offers the flexibility to perform
extensive packet manipulation: since the packet its recreated every time at the
Ingress and Egress points, while in the Network Function Virtualization
Infrastructure (NFVI), the original packet can be stripped of its headers (that
could be saved in the session table) to slightly improve internal packet
transmission. \todo{Insert TCP session recreation schema} On top of that, it
offers the possibility to use different TCP flavours, hence increasing the
communication speed in heterogeneous networks (e.g. in case of satellite
connections TCP Hybla can be employed, while it is known that HighSpeed TCP
gives best results when applied in optical fiber-based connections).

>>>>

As today, when a packets gets send from a seder $S$, to a receiver $R$, the 
packet gets travelling to te backbone receive appropriate in-hardware packet 
processing before being received by $R$. During this elaboration, it is 
important to maintain the transparency of the connection, so that the network 
users are not aware of the packets elaboration at all. To perform that, many 
solutions are available: TUN/TAP packet incapsulation, IP Encapsulation within 
IP or TCP session recreation (know also as TCP split).

TUN/TAP and IP Encapsulation within IP (initially defined in RFC 2003 with the 
aim to deliver IP packets over Mobile IP for mobile networks) maintain the 
connection transparency incapsulating the packet in another one.
\begin{figure}[t]
  \centering
  \includegraphics[scale=0.5]{IPoverIP}
  \caption[IP Encapsulation within IP packet schema]{An schema of IP 
Encapsulation within IP. Is noticeable how the original packet becomes the 
payload of a new one, thus being encapsulated. All the informations regarding 
the original packet remains untouched: when this kind of packet gets send 
from a machine to another, the OS will remove the new packet header and will 
present to the user-space program receiving the data its payload: a IP 
packet. Packets encapsulation can be applied with higher layers too, thus 
allowing for TCP and UDP packet incapsulation.}
  \label{chap:prjan:img:ip_over_ip}
\end{figure}

In this way, the original packet remains preserved and it becomes the new packet
payload, that can be elaborated and modified accordingly, until it gets 
decapsulated and sent to $R$ eventually. When $R$ receives the packet, it is 
not be aware of the packet elaboration, since all the original headers were 
preserved (or slightly modified). In particular, IP Encapsulation within IP 
allow the packets to make intermediate destinations that otherwise would not be 
selected.
TCP session recreation, instead, ``split'' the TCP session in two endpoints: an 
Ingress, that manage the connection with the client and an Egress, that 
communicate with the packet receiver creating a multi-overlay-hop path where 
for each hop there is an possible indipendent TCP connection. In order to 
achieve that, a session table needs to be established and continuously updated, 
while TCP headers need to be accordingly modified to allow data transmission 
through the Ingress and Egress points. Nonetheless, care should be given to 
packets path: in order to avoid ill-calculated congestion windows, the incoming 
packets need to follow the same (or an equivalent one) path for the same 
instatiated connection. This phenomenom is based on the intermediate proxies 
that create the route: it is the case, for example, when an intermediate node 
sends back a spoofed ACK before the original packet is delivered to the real 
consegnee. In this senario, the sender, unaware of the proxy, will miscalculate 
the sending window based on the too low RTT.
Other problems of TCP splitting are reliability and security, especially because
the end to end TCP logic is no longer maintained: a server failure may cause to
an unaware client to believe that all the packets have reached the destination.
TCP session recreation seems burdersome and it doesn't seem to add any
significant benefit at the first sight, but it offers the flexibility to perform
extensive packet manipulation: since the packet its recreated every time at the
Ingress and Egress points, while in the Network Function Virtualization
Infrastructure (NFVI), the original packet can be stripped of its headers (that
could be saved in the session table) to slightly improve internal packet
transmission. \todo{Insert TCP session recreation schema} On top of that, it
offers the possibility to use different TCP flavours, hence increasing the
communication speed in heterogeneous networks (e.g. in case of satellite
connections TCP Hybla can be employed, while it is known that HighSpeed TCP
gives best results when applied in optical fiber-based connections).
